Trap spaces of Boolean networks are conflict-free siphons of their Petri net encoding

### 2023-06-16 manuscripts/TCS2023/tcs2023.tex
Reference for BBM repository

\change{The research group behind the \texttt{BBM} repository has recently undertaken considerable effort for building a collection of real-world Boolean models from various sources used in systems biology.}
It aims to be a comprehensive collection suitable for benchmarking and testing new tools and methods.
\texttt{BBM} consists of 211 models (24 out of them are non-locally-monotonic), peaking at 321 nodes, 1100 regulations among the nodes, and 133 source nodes, respectively.
It is released and maintained at \url{https://github.com/sybila/biodivine-boolean-models}.
We here tested all the compared methods on this model repository.

>>>>

\change{The research group behind the \texttt{BBM} repository~\cite{pastva2023repository} has recently undertaken considerable effort for building a collection of real-world Boolean models from various sources used in systems biology.}
It aims to be a comprehensive collection suitable for benchmarking and testing new tools and methods.
\texttt{BBM} consists of 211 models (24 out of them are non-locally-monotonic), peaking at 321 nodes, 1100 regulations among the nodes, and 133 source nodes, respectively.
It is released and maintained at \url{https://github.com/sybila/biodivine-boolean-models}.
We here tested all the compared methods on this model repository.
